\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-06 response.tex

\tba

10. page 10, Claim 5: Indices could mostly be removed by continuing
to talk about $T$-ancestors instead. Move the definition of $H+$ and its
directed version up, along with the explanation of what will be proven,
so that it isn’t necessary to define the $s_i$.

\tba

11. page 10, Claim 5: The name $P_{ww'}$ is strange since in case 2. there is
no $w'$ defined.

\textcolor{blue}{Rearranged the sentence so that it is more clear we are defining $w'=w$. }

@@

Page 13.  Regarding the proof of Lemma 4, I think it is better to
include all the details from reference [14].  As far as I know, JCTB
does not have a page limit, so I do not see an issue with just
reproducing the entire proof and telling the reader that they can skip
all the details if they wish.  This is just my personal opinion
though, so the authors can ignore this request if they choose.

\tba

Page 15. Regarding the proof of Theorem 11, if it really is the same
proof as the proof of Theorem 2, why not just prove Theorem 11 (from
which Theorem 2 follows as a special case)?

\textcolor{blue}{We have written the entire paper starting with simpler cases before moving onto the more general. This approach may use a few more words, but we think the paper becomes more accessible for more readers this way.}

@@

Page 18.  Replace '$|i'-i''| < p$' by  '$0< |i'-i''| < p$'.

\tba

Page 20.  Where does the bound $d(d-3)/2$ come from?  The naive bound I
compute is $d(d-1)/2$.

\textcolor{blue}{By construction, if the path $vxw$ is in $\mathcal{P}$, then $xv$ and $xw$ are non-consecutive edges incident to $x$. The bound of $d(d-1)/2$ arises if one ignores that $xv$ and $xw$ are non-consecutive.}

### 2022-03-06 k-planar.tex
more updates

\usepackage{doi} % To make plainnat handle doi's properly

@@

@@

\begin{figure}[!h]
\centering%	\begin{center}
	\includegraphics{ProductExample}
	%\end{center}
	\caption{Example of a strong product.
	\label{ProductExample}}
\end{figure}

@@

@@

\begin{thm}[\citep{DJMMUW20}]
	\label{GenusProduct}
	Every graph of Euler genus $g$ is a subgraph of:
	\begin{compactenum}[(a)]
		\item $H  \boxtimes P$ for some graph $H$ of treewidth at most $2g+8$  and some path $P$.
		\item $H \boxtimes P \boxtimes K_{\max\{2g,3\}}$ for some graph $H$ of treewidth at most $4$ and for some path $P$.\label{temp}
	\end{compactenum}
\end{thm}

@@

\note{DW}{I think $\binom{k+t}{t}$ in \cref{general-bag-size} and $\binom{p+t}{t}$ in \cref{p-centered-treewidth} are no coincidence. The proofs are very similar. Worth exploring further?}

@@

\referee{2}{Page 20.  Where does the bound $d(d-3)/2$ come from?  The naive bound I
compute is $d(d-1)/2$.}
\note{DW}{consecutive neighbours don't have to be counted. I will revise}

@@

\subsection*{Note Added in Proof} Subsequent to the initial release of this paper, the treewidth 8 bound in \cref{PlanarProduct} was improved to 6 by \citet{UWY}, which implies that the treewidth $2g+8$ bound in \cref{GenusProduct}(a) can be improved to $2g+6$. Simmilarly, the treewidth 4 bound in \cref{GenusProduct}(b) was improved to 3 by \citet{DHHW}. \note{DW}{Say more about the consequence for the bounds in the rest of the paper}

@@

\end{document}

>>>>

%\usepackage{doi} % To make plainnat handle doi's properly

@@

\note{DW}{I suggest we replace $8$ by $6$ here, and replace ``The starting point for this work is the following `product structure theorem' for planar graphs by \citet{DJMMUW20} (improved by \citet{UWY})''. Okay?}

@@

\begin{figure}[!h]
\centering
\includegraphics{ProductExample}
\caption{Example of a strong product.
\label{ProductExample}}
\end{figure}

@@

\note{DW}{Add \citep{EJM} to the story.}

@@

\begin{thm}[\citep{DJMMUW20}]
	\label{GenusProduct}
	Every graph of Euler genus $g$ is a subgraph of:
	\begin{compactenum}[(a)]
		\item $H  \boxtimes P$ for some graph $H$ of treewidth at most $2g+8$  and some path $P$.
		\item $H \boxtimes P \boxtimes K_{\max\{2g,3\}}$ for some graph $H$ of treewidth at most $4$ and for some path $P$.
	\end{compactenum}
\end{thm}

\note{DW}{I suggest we replace $2g+8$ by $2g+6$ here and replace 4 by 3, and cite \citep{DHHW,UWY}. This will improve the bounds and (more importantly) simplify the presentation of various results (such as \cref{StringPartition,PowerGenus}) which currently distinguish the $g=0$ case. }

@@

@@

@@

%\subsection*{Note Added in Proof} Subsequent to the initial release of this paper, the treewidth 8 bound in \cref{PlanarProduct} was improved to 6 by \citet{UWY}, which implies that the treewidth $2g+8$ bound in \cref{GenusProduct}(a) can be improved to $2g+6$. Simmilarly, the treewidth 4 bound in \cref{GenusProduct}(b) was improved to 3 by \citet{DHHW}. \note{DW}{Say more about the consequence for the bounds in the rest of the paper}

@@

\end{document}s
